---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Kmeans

<!-- badges: start -->
[![Author](https://img.shields.io/badge/Author-KexinLi-red.svg "Author")](https://kexiin.gitee.io "Author")
<!-- badges: end -->

The goal of Kmeans is to partition a dataset into distinct, non-overlapping groups or clusters. Each data point is assigned to one of these clusters based on its similarity to the centroid (center) of the cluster. The algorithm aims to minimize the intra-cluster variance, meaning that the data points within a cluster should be as similar as possible.

## Installation

You can install the development version of Kmeans from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("kexiin/BIOSTAT625_Kmeans")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(Kmeans)

dataSet <- rbind(matrix(rnorm(100, 0.5, 1), ncol = 2), matrix(rnorm(100, 2, 0.1), ncol = 2))
KMeans(dataSet, kclust=2, do.plot=TRUE)
```

To comparison correctness against the original R function in base library `kmeans`:

```{r}
KMeans(dataSet, kclust=2)$centroids
kmeans(dataSet, 2)$centers
```

The output centers are very similar, indicating that the accuracy of this algorithm is relatively high.  

To comparison efficiency against the original R function in base library `kmeans`:
```{r}
dataSet <- rbind(matrix(rnorm(1000, 0.5, 1), ncol = 2), matrix(rnorm(1000, 2, 0.1), ncol = 2))
system.time({KMeans(dataSet, kclust=2, do.plot=TRUE)})
system.time({kmeans(dataSet, 2)})
```

It can be seen from the calculation time that the efficiency of this algorithm is not as efficient as `kmeans` in the base library and needs to be further enhanced.

